\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Add colon before list
Fix grammar

It is possible to upgrade both the transaction validation rules, and the current state of the chain, through the transaction processing system itself. This is typically enabled by having the transaction validation rules be stored in the state, and run them on top of some virtualization layer. This property is a requirement for the following

@@

In the BRAQ model, two parameters are required for each action, the \textit{range length}, denoted by $R$, and the \textit{action quota}, denoted by $Q$, both being positive integers. A combined range length and transaction limit is called a \textit{BRAQ quota}. The model prevents an action in a given block if there are already $L$ such actions in the current to $R$ blocks back. The system must maintain a sequence of positive integers $H=(h_1, \ldots, h_N)$, called the \textit{event list}, for each action. Initially set to an empty list. A combined BRAQ quota and such list is called \textit{BRAQ instance}.
An action should not be allowed in block height $h$ when

>>>>

It is possible to upgrade both the transaction validation rules, and the current state of the chain, through the transaction processing system itself. This is typically enabled by having the transaction validation rules be stored in the state, and run them on top of some virtualization layer. This property is a requirement for the following:

@@

In the BRAQ model, two parameters are required for each action, the \textit{range length}, denoted by $R$, and the \textit{action quota}, denoted by $Q$, both being positive integers. A combined range length and transaction limit is called a \textit{BRAQ quota}. The model prevents an action in a given block if there are already $L$ such actions in the current to $R$ blocks back. The system must maintain a sequence of positive integers $H=(h_1, \ldots, h_N)$, called the \textit{event list}, for each action, initially set to an empty list. A combined BRAQ quota and such list is called \textit{BRAQ instance}.
An action should not be allowed in block height $h$ when
